\documentclass[a4paper,12pt]{article}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\setlength\overfullrule{5pt}

\newcommand{\pois}[1]{}
\title{ Weekly Exercise 2}
\author{Shubo Yan }
\date{12.9.2017}
\begin{document}
	\maketitle
\newpage
\section{Question 1}
\subsection*{A{\small RTHUR} C. C{\small LARKE}}

{\LARGE S{\Large IR} A{\Large RTHUR} C{\Large HARLES} C{\Large LARKE}\par}

\begin{itemize}	
\item Lived at 16 December 1917--19 March 2008
\item Alma mater: King's College London
\item Career:
\begin{enumerate}
\item a British science  action writer,
\item science writer and futurist,
\item inventor,
\item undersea explorer,
\begin{flushleft}
and
\end{flushleft}
\item television series host	
\end{enumerate}	
\end{itemize}	

He is famous for being co-writer of the screenplay for the 1968 film 2001: A Space Odyssey, widely considered to be one of the most influential films of all time.
\begin{quote}
\textit{Clarke was a science writer, who was both an avid populariser of space travel and a futurist of uncanny ability. On these subjects he wrote over a dozen books and many essays, which appeared in various popular magazines.}
\end{quote}
In 1961 he was awarded the \textbf{Kalinga Prize}, an award which is given by UNESCO for popularizing science. These along with his science fiction writings eventually earned him the moniker ``Prophet of the Space Age''. His other science fiction writings earned him a number of Hugo and Nebula awards, which along with a large readership made him one of the towering figures of science fiction.

For many years \underline{Clarke, Robert Heinlein and Isaac Asimov} were known as the ``Big Three'' of science fiction.
\pagebreak

\section{Question 2}
\subsection*{\centering Biography}
\begin{center}
Early years
\end{center}

Clarke was born in Minehead, Somerset, England, and grew up in nearby Bishops Lydeard.
\begin{flushright}
As a boy, he grew up on a farm enjoying stargazing, fossil collecting, and reading American science  ction pulp magazines.
\end{flushright}
\begin{flushleft}
He received his secondary education at Huish Grammar school in Taunton. Early in uences included dinosaur cigarette cards, which led to an enthusiasm for fossils starting about 1925.
\end{flushleft}

\begin{itemize}
\item   Clarke attributed his interest in science fiction to reading three items: the November 1928 issue of Amazing Stories, in 1929; Last and First Men by Olaf Stapledon in 1930; and The Conquest of Space by David Lasser in 1931.
\end{itemize}
{\raggedright In his teens, he joined the Junior Astronomical Association and contributed \par}
{\raggedleft to Urania, the society's journal, which was edited in Glasgow by Marion Eadie.\par}

\noindent This paragraph has the normal -- or default -- justification, but notice that it is not indented.
\pagebreak

\section{Question 3}
{\large When is Arthur C. Clarke born? \newline He was born on 16 December 1917.\newline
What is the name of the university he graduated?\linebreak King's College London.\newline
List the most important books he has read (according to him):
before 1931  Amazing Stories and Last and First Men by Olaf Stapledon; and at 1931  The Conquest of Space by David Lasser.\par}
\section{Question 4}
\vspace{\stretch{1}}{\large This large size text is the last line of the page!\par}\pagebreak
\section{Question 5}
\newpage
\vspace*{\fill}
\hspace{\stretch{1}}This line is in the middle of the page!\hspace{\stretch{1}}
\vspace*{\fill}
\pagebreak
\section{Question 6}
\begin{tabbing}
Program\hspace{6mm} : \TeX \\[2mm]
Author(s)\hspace{5mm}: Donald Knuth \\[2mm]
Manuals\hspace{8mm}: \\[6mm]
\hspace{5mm}\textsf{Name} \=\hspace{40mm}\textsf{Author}\=\hspace{22mm}\textsf{Publisher} \\[3mm]

\hspace{5mm}The \TeX Book \>\hspace{40mm}Donald Knuth  \>\hspace{22mm}Addison-Wesley\\[3mm]

\hspace{5mm}The Advanced \TeX \ Book \>\hspace{40mm}David Salomon \>\hspace{22mm}Springer-Verlag
\end{tabbing}
\section{Question 7}
{\small
\begin{tabbing}	
\hspace*{15mm}\=\hspace*{10mm}\=%
\hspace*{5mm}\=\hspace*{5mm}\=\hspace*{5mm}\=\kill	
\textbf{public int}[ ] InsertionSort(int[ ] data)\{\\
\>\textbf{int} len = data.length;\\
\>\textbf{int} key = 0;\\
\>\textbf{int} i = 0;\\
\>\textbf{for}(\textbf{int} j = 1; j<len;j++)\{\\
\>\>key = data[j];\\
\>\>i = j-1;\\
\>\>\textbf{while}(i>=0 \&\& data[i]>key)\{\\
\>\>\>\>data[i+1] = data[i];\\
\>\>\>\>i = i-1;\\
\>\>\>\>data[i+1]=key;\\
\>\>\}\\
\>\}\\
\>\textbf{return} data;\\
\}
\end{tabbing}	
}
\end{document}
